%کلمات کلیدی انگلیسی
\latinkeywords{Artificial Intelligence, Digital Twin, Traffic Simulation, Autonomous Vehicles, Traffic Management Systems}
%چکیده انگلیسی

\en-abstract{
\begin{latin}
    In the realm of modern transportation systems, the development and testing of Intelligent Transportation Systems (ITS), traffic management algorithms, and autonomous vehicles have become paramount. Ensuring the efficacy and safety of these systems hinges on the ability to simulate real-world traffic scenarios accurately. This imperative has given rise to the concept of a "digital twin," a powerful tool adopted extensively in computer simulations.
    A digital twin serves as a dynamic virtual replica of a physical environment, offering an invaluable platform to expedite advancements in autonomous vehicle technology and traffic management. Beyond its application in autonomous vehicles, digital twins find utility in a broader spectrum of domains, including ITS systems and traffic management systems. This is especially relevant when evaluating the performance of algorithms and strategies within a simulated but realistic traffic context. Traffic simulations play an indispensable role in training the driving logic of autonomous vehicles, ensuring their adaptability to region-specific, dynamic traffic conditions.
    Traditionally, the creation of traffic conditions in simulations has been achieved through manual methods or synthesized using mathematical models. However, these approaches often fall short in replicating the nuanced, region-specific complexities of real-world traffic. Moreover, they entail labor-intensive efforts. This research delves into an innovative and practical approach to address these challenges. We propose an automatic methodology that leverages sensor data, particularly Lidar sensor data, and employs artificial intelligence algorithms for 3D object detection. This methodology enables the accurate simulation of various real-world traffic scenarios.
\end{latin}
}
%%%%%%%%%%%%%%%%%%%%% کدهای زیر را تغییر ندهید.

\newpage
\thispagestyle{empty}
\begin{latin}
\section*{\LARGE\centering Abstract}

\een-abstract

\vspace*{.5cm}
{\large\textbf{Key Words:}}\par
\vspace*{.5cm}
\elatinkeywords
\end{latin}